\documentclass{article}
\usepackage[utf8]{inputenc}

\title{OpenRefine-Journal-JeremyAmin}
\author{Jeremy Amin}
\date{September 2019}

\begin{document}

\maketitle

\section{Working with OpenRefine}

\subsection{Entry 1: 13 SEPT 2019}

\begin{enumerate}
\item Transformed `interview\textunderscore date' to `To date'. Opened a `Text facet' and found 19 entries.
\item Opened `Timeline facet' for `interview\textunderscore date' and found that the most number of interviews were conducted between the 16th and the 27th of NOV 2016.
\item Opened `Text facet' and corrected the naming errors. Ended up with four names: Chirodzo, God, Ruaca and 49.
\item Transformed the text in `items\textunderscore owned' column to remove right and left brackets, single suote marks, and spaces.
\item Did `custom text facets' for `items\textunderscore owned'. In the Expression box  typed `value.split(";")'. In the facet I was able to arrange by `count' and see the number of entries for each item in the list.
\item Cleaned up the `months\textunderscore lack\textunderscore food' and found that November was the most common month for respondents to lack food.
\end{enumerate}

\section{Filtering and Sorting with OpenRefine}
\subsection{Entry 1: 4 OCT 2019}

\begin{enumerate}
    \item Did text filter and typed `mabat'. Successfully filtered mabatipitched and mabatisloping.
    \item Opened up `Text facet' and performed the `include' and `exclude' functions in the `Excluding entries' exercise.
    \item For the `Sort' exercise I sorted by numbers from smallest to largest. The first ten cells had zero as the number. This suggests possibly a black input which resulted in the program correcting it to zero.
    \item Sorted the `gps\textunderscore Longitude' and gps\textunderscore Lattitude by number from largest to smallest. Found the `Village' named `49'. Once I moved the `Village' column near the `gps\textunderscore Longitude' and `gps\textunderscore Lattitude' columns I then moved `Village' back to the beginning of the spreadsheet and compared cell containing `49' with the `interview\textunderscore date' column with the same lattitude and longitude and found that only interviews in Chirodzo were held on that date. So `49' must be `Chirodzo'.
    \item 
\end{enumerate}

\section{Examining Numbers in OpenRefine}

\subsection{Entry 1: 4 OCT 2019}

\begin{enumerate}
    \item Transformed the four columns in the `Numbers' exercise to 'To number'. Couldn't transform `Village' column to numbers.
    \item In `Numeric facet' exercise I changed two cells. One to `abc' and one i made blank. The Numeric facet option allowed me to isolate the non-numeric and blank cells and filter them out of the column.
    \item Peformed the `Undo' function to return cells to their original numeric inputs.
\end{enumerate}

\section{Using scripts}

\subsection{Entry 1: 4 OCT 2019}

\begin{enumerate}
    \item Extracted the script from my cleaned data set and applied it to a new OpenRefine project with the original messy dataset.
\end{enumerate}

\section{Exporting and Saving Data from OpenRefine}

\subsection{Entry 1: 4 OCT 2019}

\begin{enumerate}
    \item Exported the project onto my MacBook.
    \item Opened up the downloaded tar.gz file and saw the `history' folder alongside a few zip files and text files.
    \item Exported the cleaned data as a csv file.
\end{enumerate}

\section{Other Resources in OpenRefine}

\subsection{Entry 1: 4 OCT 2019}

I looked at the `Using OpenRefine' book. I like how it is written like a cook book! Seems like a nice and user friendly way to make OpenRefine accessible to the average level computer user.

\end{document}
